Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-09-09 paper/main.tex
fixed some typos

The LP solver now returns a solution of the constraint set and an
objective value, that is, a mapping from variables to floating-point
numbers and the value of the objective function with this
instantiation.  The solver also memorizes the optimization path that
lead to the optimal solution.  In this case, the objective value would
be
$
5000
$
since the LP solver assigns $q_{0,x} = 0.5$ and $q_{*} = 0$ otherwise.
We now add the constraint
$$
q_{x,0} + 10000{\cdot}q_{0,x} + 10{\cdot}q_{x,10} + 9990q_{10,x} = 5000
$$
to our constraint set and ask the solver to optimize the objective
function
$$
q_0 + 11{\cdot}q_{0,10} \; .
$$
This happens in almost no time in practice.

@@

Another interesting note is that the constraints that we generate have
a particularly simple form that is know as \emph{network problem}.
Such problems can be solve in linear time in practice.

>>>>

The LP solver now returns a solution of the constraint set and an
objective value, that is, a mapping from variables to floating-point
numbers and the value of the objective function with this
instantiation.  The solver also memorizes the optimization path that
led to the optimal solution.  In this case, the objective value would
be
$
5000
$
since the LP solver assigns $q_{0,x} = 0.5$ and $q_{*} = 0$ otherwise.
We now add the constraint
$$
q_{x,0} + 10000{\cdot}q_{0,x} + 10{\cdot}q_{x,10} + 9990q_{10,x} = 5000
$$
to our constraint set and ask the solver to optimize the objective
function
$$
q_0 + 11{\cdot}q_{0,10} \; .
$$
This happens in almost no time in practice.

@@

Another interesting note is that the constraints that we generate have
a particularly simple form that is known as \emph{network problem}.
Such problems can be solved in linear time in practice.
